The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-04-05 background.tex
添加了逻辑图，改善文章结构，主要在方法上

% !TEX root = Eco-Model.tex
\section{Problem Background} % (fold)
\label{sec:problem_background}

\subsection{Cloud Manufacturing Ecosystem} % (fold)
\label{sub:cloud_manufacturing_ecosystem}
As an application of Networked Manufacturing, Cloud Manufacturing proposed by ...

(problems background to form the ecosystem)

Combined with the problem background and other scholars' previous work, we proposed an improved framework that suits for Cloud Manufacturing environment as shown in \autoref{fig:structure}.
\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
\caption{Cloud Manufacturing Architecture with Main Flows}
\label{fig:structure}
\end{figure}

The architecture of Cloud Manufacturing is mainly composed of three parts, namely, \begin{inparaenum}[1)]
\item User,
\item Platform and
\item Physical Base
\end{inparaenum}, that are connected by material or information flows. A simple version of conception for Cloud Manufacturing architecture we study here can be described as follows:
\begin{compactdesc}
\item [User] part describes the main roles in the Cloud Manufacturing environment like manufacturing service provider and manufacturing service demander, whome can be called as provider and demander for short respectively, from the functional point of view. Meanwhile, these roles can also be classified into enterprise user and customer, from the practical point of view. Both functional and practical are important perspective for later analysis in following sections. 
\item [Platform] part consists of 3 main layers namely \begin{inparaenum}[1)]
\item Application/Interface Layer,
\item Service Layer and 
\item Resource \& Production Layer
\end{inparaenum}.
Service is the core idea of Cloud Manufacturing, so Service Layer is the core of the Cloud Manufacturing platform. With the help of related technology in servitization, manufacturing resource and production can be encapsulated into services, then these services can be acquired by users with the well designed applications or interfaces.
\item [Physical Base] part includes the basic infrastructure, resource and production. It's worth mentioning that part of resources and production can even be virtualized with some services the platform provides.
\end{compactdesc}

\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
\caption{Supplementay Illustration for \autoref{fig:structure}}
\label{fig:supplementary}
\end{figure}

With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in Cloud Manufacturing environment with the forementioned flows that marked by circled number (i.e. \textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the Cloud Manufacturing system. In \autoref{fig:supplementary}, we denote provider, demander, platform and physical base as \textbf{P}, \textbf{D}, \textbf{PF} and \textbf{PB} respectively. The overlap among application districts implies the complexity of the system, so that we will analyse these applications coordinately from a system view.

Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

\subsubsection{Enterprise Business Mode}

\subsubsection{Resource Sharing Mechanism}

\subsubsection{Ecosystem Adjustment}

@@

\subsection{Main Copmlexity Concepts} % (fold)
\label{sub:main_copmlexity_concepts}

@@

\subsubsection{Adaption}
% subsection main_copmlexity_concepts (end)

\subsection{Ecosystem Evolvement} % (fold)
\label{sub:ecosystem_evolvement}

@@

\subsection{Optimal Guidance} % (fold)
\label{sub:optimal_guidance}

% subsection optimal_guidance (end)
% section problem_background (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Background} % (fold)
\label{sec:background}

\subsection{Origin and description of the research problem} % (fold)
\label{sub:origin_and_description_of_the_problem}

As an application of networked manufacturing, cloud manufacturing proposed by ...

(problems background to form the ecosystem)
% subsection origin_and_description_of_the_problem (end)

\subsection{Cloud manufacturing ecosystem} % (fold)
\label{sub:cloud_manufacturing_ecosystem}

\subsubsection{Cloud manufacturing ecosystem architecture}

Combined with the background of the research problem and other scholars' previous study in cloud manufacturing, we proposed an improved framework that suits for cloud manufacturing environment as shown in \autoref{fig:structure}.
\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 35]{Cloud_Mfg_Structure.pdf}
\caption{Cloud manufacturing architecture with main flows}
\label{fig:structure}
\end{figure}

The architecture of cloud manufacturing is mainly composed of three parts, namely, \begin{inparaenum}[1)]
\item user,
\item platform and
\item physical base
\end{inparaenum}, that are connected by material or information flows. A simple version of conception for cloud manufacturing architecture we study here can be described as follows:
\begin{compactdesc}
\item [User] part describes the main roles in the cloud manufacturing environment like manufacturing service provider and manufacturing service demander, whome can be called as provider and demander for short respectively, from the functional point of view. Meanwhile, these roles can also be classified into enterprise user and customer, from the practical point of view. Both functional and practical are important perspective for later analysis in following sections. 
\item [Platform] part consists of 3 main layers namely
	\begin{inparaenum}[1)]
	\item application/interface layer,
	\item service layer and 
	\item resource \& production layer
	\end{inparaenum}.
Service is the core concept in cloud manufacturing, so service layer is the core in the cloud manufacturing platform. With the help of related technology in servitization, manufacturing resource and production can be encapsulated into services, then these services can be acquired by users with the well designed applications or interfaces.
\item [Physical Base] part includes the basic infrastructure, resource and production. It's worth mentioning that part of resources and production can even be virtualized with some services the platform provides.
\end{compactdesc}

\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
\caption{Supplementay illustration for \autoref{fig:structure}}
\label{fig:supplementary}
\end{figure}

With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in cloud manufacturing environment with the forementioned flows that marked by circled number (i.e. \textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the cloud manufacturing system. In \autoref{fig:supplementary}, we denote provider, demander, platform and physical base as \textbf{P}, \textbf{D}, \textbf{PF} and \textbf{PB} respectively. The overlap among application districts implies the complexity of the system, so that we will analyse these applications coordinately from a systematic view.

\subsubsection{Operation model}
% 放那两张流程图，以说明流程。分别作为平台及企业自生的运作模式
\begin{figure}[!h]
\centering\small
% \subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
% \subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
\resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
\caption{Simple Flow Chart of Order}
\label{fig:simpleorderflow}
\end{figure}
\subsubsection{Main features in the ecosystem}
% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。
As shown in \autoref{fig:structure}, 
Rating system, decision support system, recommender system,
detail info will seen in
Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

@@

\subsection{Main complexity concepts} % (fold)
\label{sub:main_complexity_concepts}

@@

\subsubsection{Adaption}
% subsection main_complexity_concepts (end)

\subsection{Ecosystem evolvement} % (fold)
\label{sub:ecosystem_evolvement}

@@

\subsection{Optimal guidance} % (fold)
\label{sub:optimal_guidance}

% subsection optimal_guidance (end)
% section background (end)

### 2016-04-05 method.tex
adjust the structure
modify the section to valide
添加了逻辑图，改善文章结构，主要在方法上

% !TEX root = Eco-Model.tex
\section{Methodological Approach} % (fold)
\label{sec:methodological_approach}

@@

\subsubsection{Assumptions and Notation}

Ecosystem application model including:
\subsubsection{Enterprise Model}

@@

@@

\subsubsection{Management Model}

@@

\subsection{Mathematical Formulation} % (fold)
\label{sub:mathematical_formulation}
\subsubsection{Comprehended Model}
% subsection mathematical_formulation (end)

\subsection{Model Validation} % (fold)
\label{sub:model_validation}

% subsection model_validation (end)

% section methodological_approach (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Methodological approach} % (fold)
\label{sec:methodological_approach}

@@

\subsubsection{Assumptions and notation}

Ecosystem application model including:
\subsubsection{Enterprise model}

@@

\subsubsection{Main modules design}
\label{subsub:main_modules}

@@

@@

% \subsection{Mathematical Formulation} % (fold)
% \label{sub:mathematical_formulation}
% \subsubsection{Comprehended Model}
% % subsection mathematical_formulation (end)

% \subsection{Verification and Validation} % (fold)
% \label{sub:verification_and_validation}

% % subsection verification_and_validation (end)

\subsection{Agent-based modeling and simulation} % (fold)
\label{sub:agent_based_modeling_and_simulation}
\subsubsection{Agent design}

\subsubsection{Logical process}
\begin{figure}[htbp]
\centering\small
\subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
\subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
% \resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
\caption{Simple Flow Chart of Order}
% \label{fig:simpleorderflow}
\end{figure}

\subsubsection{Interaction among agents}
some mathematical formulation display here to describe the whole ecosystem wide phenomenon, like Little formulation.

\subsubsection{Verification and validation}
% subsection agent_based_model_and_simulation (end)
% section methodological_approach (end)
